Mice synthesizing with partitioned data

### 2020-08-08 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Adjusted degrees of freedom for partitioned data.

>>>>

# Adjusted degrees of freedom

Alternatively, we can alter the minimum value for the degrees of freedom to $\text{max}(m - 1, \nu)$, as is done in Reiter and Drechsler (2010) as well.

This approach yields the following results with `maxit` set to 1.

```{r, include = F}
source("functions.R")
```

```{r}
boot_parts %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool2.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

And the following results when we fix `maxit` at five.

```{r}
boot_parts_5 %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool2.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
